---
title: "Meta-Analysis_Kinesiophobia_Physical_Activity"
author: "IM Lahart, MP Boisgontier"
date: "`r format(Sys.Date(),'%e de %B, %Y')`"
output:
  pdf_document:
    latex_engine: xelatex
    toc: yes
    toc_depth: 3
---
<style>
body{
  font-size: 8pt;
}
</style>
---

# R Markdown file set-up and packages

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Packages required:
1) dmetar
2) tidyverse
3) meta
4) metafor
5) metasens
6) esc

```{r install and load dmetar, include=FALSE}
if (!require("devtools")) {
  install.packages("devtools")
}
devtools::install_github("MathiasHarrer/dmetar")
library(dmetar)
```

```{r packages, include=FALSE}
#Install tidyverse package if needed for 'glimpse'
if(!require(tidyverse)){install.packages('tidyverse')}
#Load tidyverse package
library(tidyverse)

#Install meta package if needed for meta-analysis
if(!require(meta)){install.packages('meta')}
#Load meta package
library(meta)

#Install metafor package if needed for meta-analysis
if(!require(metafor)){install.packages('metafor')}
#Load metfor package
library(metafor)

#Install esc package if needed for Fisher z conversion to r
if(!require(esc)){install.packages('esc')}
#Load esc package
library(esc)


```


# Meta-analysis method
We pooled Pearson product-moment correlations from eligible studies to examine the relationship between kinesiophobia and physical activity. Correlations were pooled using the generic inverse pooling method via the ‘metacor’ function in the {meta} R package. This function automatically performs a necessary Fisher’s z-transformation on the original, untransformed correlations prior to pooling. The ‘metacor’ function also reconverts the pooled association back to its original form for ease of interpretation. Correlation estimates were nested within studies using the ‘cluster’ argument to account for the dependencies between these estimates, resulting in a three-level meta-analysis (level 1: participants, level 2: correlation estimates, level 3: studies). The distribution of variance across levels was assessed using the multilevel version of I2. The performance of the 2-level and 3-level meta-analyses was assessed and compared using the {metafor} R package.

We anticipated considerable between-study heterogeneity, and therefore used a random-effects model to pool correlations. The restricted maximum likelihood (RML) estimator (Viechtbauer, 2005) was used to calculate the heterogeneity variance Tau2. In addition to Tau2, to quantify between-study heterogeneity, we report the I2 statistic, which provides the percentage of variability in the correlations that is not caused by sampling error56. The I2 statistic was interpreted as follows: 0-40%, may not be important; 30-60%, may represent moderate heterogeneity; 50-90%, may represent substantial heterogeneity; and 75-100%, may represent considerable heterogeneity. To reduce the risk of false positives, we used a Knapp-Hartung adjustment (Knapp and Hartung, 2003) to calculate the confidence interval around the pooled association. We also report the prediction interval, which provides a range within which we can expect the associations of future studies to fall based on the current evidence. The pooled correlation was interpreted using Cohen’s conventions (Cohen, 1988): r ≈ -0.10, small negative correlation; r ≈ -0.30, moderate negative correlation; r ≈ -0.50, large negative correlation.

Publication bias was assessed using a funnel plot, which is a scatter plot of the studies’ effect size expressed as the Fisher’s z transformed correlation on the x-axis against a measure of their standard error (which is indicative of precision of the study’s effect size) on the y-axis. When there is no publication bias, the data points in a funnel plot should form a roughly symmetrical, upside-down funnel. Studies in the top part of the plot, which have lower standard errors, are expected to lie closely together, and not far away from the pooled effect size. In the lower part of the plot, studies have higher standard errors, the funnel “opens up”, and effect sizes are expected to scatter more heavily to the left and right of the pooled effect. Egger’s regression (Egger et al., 1997) can be used to formally test funnel plot’s asymmetry. However, since there is no direct function to conduct Egger's test for 3-level models, we calculated it by using the standard errors of the effect size estimates as a predictor in the meta-regression60.

P-curve analysis (Simonsohn et al., 2014) was conducted to assess whether the distribution of the statistically significant results was consistent with what would be expected if only true effects were present. When the null hypothesis is true (i.e., there is no true effect), p-values are assumed to follow a uniform distribution: highly significant effects (e.g., p = 0.01) are as likely as barely significant effects (e.g., p = 0.049). However, when the null hypothesis is false (i.e., there is a true effect in our data), p-values are assumed to follow a right-skewed distribution: highly significant effects are more likely than barely significant effects. A left-skewed distribution would suggest that some studies used statistical tests to find significant results in ways that may not be reproducible or generalizable (i.e., p-hacking).

A secondary meta-analysis was conducted using the same approach, but based on Spearman’s rho values, to further test the relationship between kinesiophobia and device-based physical activity.

Subgroup analyses were conducted to examine the differences in correlations between studies including participants with different health conditions and using different types of physical activity measures (i.e., device-based versus self-reported), physical activity measurement instruments (i.e., type of questionnaires, type of devices), physical activity outcomes, and kinesiophobia measures.

Exploratory meta-regressions were conducted to examine if the average age of participants, the proportion of women, and pain in a study predicted the reported correlation between kinesiophobia and physical activity. Pain was normalized to a 0-100 scale to make the data comparable across pain scales. A sensitivity analysis was conducted to examine whether the quality of the studies affected the results.

All analyses were performed in RStudio integrated development environment (IDE) (2023.06.1+524, “Mountain Hydrangea” release) for R software environment (R Core Team, 2023) using the ‘meta’ (Schwarzer, 2023), ‘metasens’ (Schwarzer et al., 2023), and ‘metafor’ (Vietchbauer, 2010, 2023) R packages.


# Meta-analysis: primary analysis

# Import Pearson r data

```{r import data file, include=FALSE}
Kinphob_r <- read.csv("2024-05-02_meta_analysis_kinesiophobia_r.csv", 
                      header = TRUE, sep = ",")
```

# Data file glimpse (not included in PDF)

```{r glimpse, include=FALSE}
glimpse(Kinphob_r)
```

## Primary analysis using metafor to compare models

```{r primary meta-analysis RE REML using metafor}
m.cor <- rma.mv(yi = z, # pool correlation coefficients Fishers Z transformation https://bookdown.org/mwheymans/bookmi/pooling-correlation-coefficients-1.html
                V = var.z, # sampling variance of Fisher's Z values: 1/(N−3), where N = the sample size.
                slab = author,
                data = Kinphob_r,
                random = ~ 1 | author/cor_id,
                test = "t", 
                method = "REML")
summary(m.cor)
```

### Converting Fisher's z back to Pearson's r

```{r Convert Fisher z back to Pearsons r}
round(convert_z2r(-0.1956), 2) # point estimate
round(convert_z2r(-0.2639), 2) # lower CI
round(convert_z2r(-0.1273), 2) # Upper CI
```

### Explore heterogeneity

```{r Heterogeneity}
i2 <- var.comp(m.cor)
summary(i2)
plot(i2)
```

The sampling error variance on level 1 and the value of I2 on level 2, i.e., the amount of heterogeneity variance within studies, were small (10.3% and 8.2%, respectively). The largest share of heterogeneity variance was from level 3, with between-study heterogeneity making up 81.5% of the total variation in our data. Overall, this indicates that there is considerable between-study heterogeneity, and less than one tenth of the variance can be explained by differences within studies.


### Comparing models

Reduced model in which the level 3 variance (between-study heterogeneity) is set to 0, which assumes all effect sizes are independent.

```{r level 3 variance set to zero}
l3.removed <- rma.mv(yi = z, 
                     V = var.z, 
                     slab = author,
                     data = Kinphob_r,
                     random = ~ 1 | author/cor_id,
                     test = "t", 
                     method = "REML",
                     sigma2 =  c(0, NA))

summary(l3.removed)
```

Comparing full and reduced models.

```{r Comparison of models}
anova(m.cor, l3.removed)
```

The 3-level model showed a better fit than the 2-level model with lower Akaike’s information criterion (AIC) (28.4 vs. 39.0) and Bayesian information criterion (BIC) (35.6 vs. 43.8), indicating better performance. These lower AIC and BIC are consistent with the significant likelihood ratio test (LRT) comparing the two models (χ2 = 12.67, p = 0.0004). Therefore, although the 3-level model introduces an additional parameter, this added complexity has improved our estimate of the pooled effect.

## Primary analysis using metacor

```{r Primary analysis using meta}
m <- metacor(cor = cor, 
              n = n,
              studlab = author,
              data = Kinphob_r,
              cluster = cluster,
              fixed = FALSE,
              random = TRUE,
              method.tau = "REML",
              method.random.ci = "HK",
              title = "Primary meta-analysis using metacor")

m
```

Our main meta-analysis of 63 studies, 83 Pearson’s r correlation estimates, and 12278 participants revealed a statistically significant small-to-moderate negative correlation between kinesiophobia and physical activity (r = -0.19; 95% confidence interval [95CI]: -0.26 to -0.13; p < 0.0001). However, we observed substantial-to-considerable between-study statistical heterogeneity (Tau2 = 0.06, 95CI: 0.02 to 0.09; I2 = 85.5%, 95CI: 82.6 to 87.9%), and the prediction interval ranged from r = -0.61 to 0.30, indicating that a moderate positive correlation cannot be ruled out for future studies.

## Primary meta-analysis forest plots

### Forest plot with Pearson r correlation coefficients

```{r Forest plot for primary analysis, fig.height=19, fig.width=12}
# Generate the forest plot without shading
forest(m, 
       layout = "Revman5",
            prediction = TRUE, 
            print.tau2 = FALSE,
            leftlabs = c("Author", "n"),
            xlim=c(-1.0,1.0),
            fs.hetstat = 10,
            addrows.below.overall = 2)
```



Save Forest plot:

```{r Save Forest plot main analysis}
png(file = "Main analysis forestplot.png", 
    width = 2800, height = 4000, res = 300)

forest(m, 
       xlim = c(-1.0, 0.6),
       layout = "Revman")

dev.off()
```


### Forest plot with Fisher z transformed correlation coefficients

```{r Forest plot mv kinesiophobia and PA, fig.height=18, fig.width=10}
forest(m.cor, 
       cex=0.8, 
       addpred=TRUE, 
       alim=c(-2,1),
       xlab = "Fisher-z transformed correlation",
       ilab = n,
       header="Author, Year", 
       shade=c(2,3,8,9,12,13,14,15,23,24,27,28,42,43,46,47,56,57,58,59,60,61,62,66,67,68,74,75,78,79,80)) # for alternate shading change ,code to: shade = 'zebra'
text(c(-2.62), m.cor$k+2, c("n"), cex=0.75, font=2)
```

Save plot:

```{r Save Forest plot Fisher z main analysis}
png(file = "Main analysis Fisher z forest plot.png", 
    width = 2800, height = 4000, res = 300)

forest(m.cor, 
       cex=0.8, 
       addpred=TRUE, 
       alim=c(-2,2),
       xlab = "Fisher-z transformed correlation",
       ilab = n,
       header="Author(s), Year, estimate n", 
       shade=c(1,2,4,5,12,13,14,15,23,24,34,35,36,40,41,44,45,50,51,52,53,54,55,56,65,66,69,70,71)) # for alternate shading change code to: shade = 'zebra'
text(c(-2.62), m.cor$k+2, c("n"), cex=0.75, font=2)

dev.off()
```


### Forest plot with aggregated Fisher z values

```{r Meta-analysis for aggregated values}
dat_r <- escalc(measure="ZCOR", 
                yi=z, 
                vi=var.z, 
                slab = author, 
                data=Kinphob_r)

agg <- aggregate(dat_r, 
                 cluster=author, 
                 V = vcov(m.cor, 
                 type="obs"), 
                 struct="ID", 
                 addk=TRUE)

res <- rma(yi, 
           vi, 
           method="EE", 
           data=agg, 
           digits=2)
res
```

```{r Forest Plot with Aggregated Values, fig.height=16, fig.width=9}
forest(res, 
       xlim=c(-7,5), 
       mlab="Pooled Estimate", 
       header=TRUE, 
       alim=c(-2,2), 
       slab = author, 
       ilab=ki, 
       ilab.xpos=-3.5, 
       shade = "zebra")
text(-3.5, res$k+2, "Estimates", font=2)
```

Save plot: 

```{r Save aggregated Forest plot main analysis}
png(file = "Main analysis aggregated forestplot.png", 
    width = 2800, height = 4000, res = 300)

forest(res, 
       xlim=c(-7,5), 
       mlab="Pooled Estimate", 
       header=TRUE, 
       alim=c(-2.5,2.5), 
       slab = author, 
       ilab=ki, 
       ilab.xpos=-3.5, 
       shade = "zebra")
text(-3.5, res$k+2, "Estimates", font=2)

dev.off()
```


# Secondary analysis based on Spearman's rho values

## Read in rho data

```{r Import rho data}
Kinphob_rho <- read.csv("2024-05-02_meta_analysis_kinesiophobia_rho.csv", 
                      header = TRUE, sep = ",")
```

## Secondary analysis using metafor to compare models

```{r Secondary meta-analysis based on rho values}
m.cor.rho <- rma.mv(yi = z, 
                     V = var.z, 
                     slab = author,
                     data = Kinphob_rho,
                     random = ~ 1 | author/cor_id,
                     test = "t", 
                     method = "REML")
summary(m.cor.rho)
```

```{r Convert Fisher z back to rho}
round(convert_z2r(-0.0959), 3) # point estimate
round(convert_z2r(-0.4017), 3) # lower CI
round(convert_z2r(-0.0017), 3) # Upper CI
```

Results of the secondary meta-analysis of 12 studies, 21 Spearman’s rho correlation estimates, and 2084 participants was consistent with the main meta-analysis as it showed a statistically significant small-to-moderate negative correlation between kinesiophobia and physical activity (r = -0.20; 95CI: -0.38 to -0.01; p = 0.049). However, we observed substantial-to-considerable between-study statistical heterogeneity (Tau2 = 0.10, 95CI: 0.04 to 0.28; I2 = 86.3%) and the prediction interval ranged from r = -0.71 to 0.45, indicating that a moderate positive correlation cannot be ruled out for future studies.

### Explore heterogeneity, rho

```{r Heterogeneity rho}
i2_rho <- var.comp(m.cor.rho)
summary(i2_rho)
plot(i2_rho)
```

The value of I2 Level 2, the amount of heterogeneity variance within clusters (i.e. within studies), is very low, totaling roughly 0%. The largest share, however, falls to level 3. Between-cluster (here: between-study) heterogeneity makes up I2 Level 3 = 96.8% of the total variation in our data. Overall, this indicates that there is considerable between-study heterogeneity on the third level, and very little of the variance can be explained by differences within studies.

### Compare models, rho

```{r level 3 variance set to zero rho}
l3.removed_rho <- rma.mv(yi = z, 
                     V = var.z, 
                     slab = author,
                     data = Kinphob_rho,
                     random = ~ 1 | author/cor_id,
                     test = "t", 
                     method = "REML",
                     sigma2 =  c(0, NA))

summary(l3.removed_rho)
```

```{r Comparison of models rho}
anova(m.cor.rho, l3.removed_rho)
```
 Modeling of the nested data structure was probably a good idea, and has improved our estimate of the pooled effect.
 
## Secondary meta-analysis using metacor

```{r Secondary analysis using meta rho}
m.rho <- metacor(cor = rho, 
              n = n,
              studlab = author,
              data = Kinphob_rho,
              cluster = cluster,
              fixed = FALSE,
              random = TRUE,
              method.tau = "REML",
              method.random.ci = "HK",
              title = "Secondary meta-analysis using metacor")

m.rho
```

## Secondary meta-analysis forest plots

### Forest plot for secondary analysis with Pearson r correlation coefficients

```{r Forest plot for secondary analysis rho, fig.height=8, fig.width=10}
forest(m.rho, 
       xlim = c(-1.0, 0.6),
       prediction = TRUE, 
       layout = "Revman")
```

Save plot:

```{r Save Secondary Forest plot main analysis with rho}
png(file = "Secondary analysis forest plot with meta.png", 
    width = 2800, height = 2500, res = 300)

forest(m.rho, 
       xlim = c(-1.0, 0.6),
       layout = "Revman")

dev.off()
```

### Forest plot for secondary analysis with Fisher z using metafor

```{r Secondary analysis forest plot based on rho, fig.height=6, fig.width=9}
forest(m.cor.rho, 
       cex=0.8, 
       addpred=TRUE, 
       alim=c(-3,2),
       xlab = "Fisher-z transformed correlation",
       ilab = n,
       header="Author(s), Year, estimate n", 
       shade= "zebra")
text(c(-2.77), m.cor.rho$k+2, c("n"), cex=0.75, font=2)
```

Save plot:

```{r Save Forest plot rho analysis}
png(file = "Rho analysis forestplot.png", 
    width = 3000, height = 2600, res = 300)

forest(m.cor.rho, 
       cex=0.8, 
       addpred=TRUE, 
       alim=c(-3,2),
       xlab = "Fisher-z transformed correlation",
       ilab = n,
       header="Author(s), Year, estimate n", 
       shade= "zebra")
text(c(-2.77), m.cor.rho$k+2, c("n"), cex=0.75, font=2)

dev.off()
```


# Meta-analysis: subgroup analyses

## Subgroup analysis by health status

```{r Subgroup analysis by health status using metafor}
Kinphob_r$Health_status <- as.factor(Kinphob_r$Health_status)


Health_subg <- rma.mv(yi = z, 
                      V = var.z,
                      slab = author, 
                      data = Kinphob_r,
                      random = ~ 1 | author/cor_id, 
                      test = "t", 
                      method = "REML",
                      mods = ~ Health_status)

summary(Health_subg)
```

The Test of Moderators revealed a significant difference between subgroups, F12,70 = 3.107, with p = 0.0014.

Note that the model results are printed within a meta-regression framework. This means that we cannot directly extract the estimates in order to obtain the pooled effect sizes within subgroups. The first value, the intercept (intrcpt), shows the z value when the health status was acute pain (z = -0.129). The effect in the other groups can be obtained by adding their estimate to the one of the intercept. Thus, the effect in the arthritis group is z = -0.1290 - 0.1295 = -0.258, and the one in the Cancer group is z = -0.1290 + 0.0448 = -0.0838. The same is true for the upper and lower confidence intervals.These are also Fisher z scores.


```{r Health status meta, warning=FALSE}
Health_stat_meta <- update(m, subgroup = Health_status, tau.common = TRUE)
Health_stat_meta
```

The test of subgroup differences between health status was conducted on studies comprising people with chronic (k = 35) or acute pain (k = 2), arthritis (k = 11), a cardiovascular condition (k = 10), a neurological condition (k = 8), surgery (k = 5), older age (k = 3), obstructive sleep apnea (k = 2), a pulmonary condition (k = 2), fibromyalgia (k = 2), cancer (k = 1), as well as in post-partum women (k = 1) and healthy young adults (k = 1). We found a statistical moderating effect of health status (p = 0.0014). The relationship between kinesiophobia and physical activity was statistically significant only in studies that included participants with cardiac condition (r = -0.30; 95CI: -0.47 to -0.11), arthritis (r = -0.25; 95CI: -0.39 to -0.10), a neurologic condition (r = -0.53; 95CI: -0.69 to -0.32), a pulmonary condition (r = -0.68; 95CI: -0.82 to -0.46), or older adults (r = -0.40; 95CI: -0.60 to -0.14). We found no evidence of an association between kinesiophobia and physical activity in studies that included participants with chronic pain (r = -0.07; 95CI: -0.16 to 0.01) or acute pain (r = -0.13; 95CI: -0.45 to 0.23). Statistical heterogeneity was higher in the studies comprising people with a pulmonary condition (I2 = 98.1%), arthritis (I2 = 93.4%), or older adults (I2 = 91.2%) than in the studies comprising people with a cardiac (I2 = 28.7%) or neurologic condition (I2 = 55.9%).

```{r Forest plot for subgroup by Health condition using meta, fig.height=29, fig.width=12}
forest(Health_stat_meta, 
       layout = "Revman5", 
       common = FALSE, 
       xlim = c(-1.0, 0.6), 
       prediction = TRUE, 
       fs.hetstat = 10, 
       col.subgroup = "black",
       addrows.below.overall = 2)
```

```{r Save Health condition forest plot meta}
png(file = "Health condition forest plot.png", 
    width = 2800, height = 7800, res = 300)

forest(Health_stat_meta, 
       layout = "Revman5", 
       sortvar = -TE, 
       common = FALSE, 
       xlim = c(-1.0, 0.6), 
       prediction = TRUE, 
       fs.hetstat = 10, 
       col.subgroup = "black",
       addrows.below.overall = 2)

dev.off()
```


## Subgroup analysis by physical activity measure: device vs self-report 

```{r Subgroup analysis by PA objectivity}
Kinphob_r$PA_objectivity <- as.factor(Kinphob_r$PA_objectivity)

PAobj_subg <- rma.mv(yi = z, 
                      V = var.z,
                      slab = author, 
                      data = Kinphob_r,
                      random = ~ 1 | author/cor_id, 
                      test = "t", 
                      method = "REML",
                      mods = ~ PA_objectivity)

summary(PAobj_subg)
```

The effect the objective measures group is z = -0.132, and in the self-report group it is z = -0.132 - .090 = -0.222.


```{r Subgroup analysis by PA objectivity meta}
PAobj_meta <- update(m, subgroup = PA_objectivity, tau.common = TRUE)
PAobj_meta
```

The test of subgroup differences between self-reported (k = 54) and device-based (k = 29) measures of physical activity showed no evidence of a moderating effect of the type of physical activity measure (p = 0.171). Both self-reported measures (r = -0.22; 95CI: -0.29 to -0.14; I2 = 89.3%) and device-based measures (r = -0.13; 95CI: -0.24 to -0.02; I2 = 57.2%) showed a negative association between kinesiophobia and physical activity.

```{r PA measure objectivity subgroup forest plot, fig.height=21, fig.width=10}
forest(PAobj_meta, 
            layout = "RevMan5", 
            common = FALSE, 
            xlim = c(-1.0, 0.6), 
            prediction = TRUE, 
            fs.hetstat = 10,
            col.subgroup = "black",
            addrows.below.overall = 2)
```

```{r Save PA objectivity forestplot}
png(file = "PA objectivity forestplot.png", 
    width = 2800, height = 5800, res = 300)

forest(PAobj_meta, 
            layout = "RevMan5", 
            common = FALSE, 
            xlim = c(-1.0, 0.6), 
            prediction = TRUE, 
            fs.hetstat = 10,
            col.subgroup = "black",
            addrows.below.overall = 2)

dev.off()
```


## Subgroup analysis by physical activity measurement instruments

```{r Subgroup analysis by PA measure}
Kinphob_r$PA_measure <- as.factor(Kinphob_r$PA_measure)

PAmeas_subg <- rma.mv(yi = z, 
                      V = var.z,
                      slab = author, 
                      data = Kinphob_r,
                      random = ~ 1 | author/cor_id, 
                      test = "t", 
                      method = "REML",
                      mods = ~ PA_measure)

summary(PAmeas_subg)
```

```{r PA measurement method meta-analysis meta, warning=FALSE}
PAm <- update(m, 
       subgroup = PA_measure, 
       tau.common = TRUE)
PAm
```

We also found no evidence of a moderating effect of physical activity instruments (p = 0.209), physical activity outcome (p = 0.685), or kinesiophobia instrument (p = 0.452).

```{r Forest plot for subgroup by PA measure, fig.height=30, fig.width=9}
forest(PAm, 
            layout = "Revman5", 
            common = FALSE, 
            xlim = c(-1.0, 1.0), 
            prediction = TRUE, 
            fs.hetstat = 10, 
            col.subgroup = 'black',
            addrows.below.overall = 2)
```


```{r Save PA measure forestplot}
png(file = "Physical activity measure forestplot.png", 
    width = 2800, height = 8400, res = 300)

forest(PAm, 
        layout = "Revman5", 
        sortvar = -TE, 
        common = FALSE, 
        xlim = c(-1.0, 1.0), 
        prediction = TRUE, 
        fs.hetstat = 10, 
        col.subgroup = 'black',
        addrows.below.overall = 2)

dev.off()
```

## Subgroup analysis by physical activity outcome

```{r Subgroup analysis by PA outcome}
Kinphob_r$PA_outcome <- as.factor(Kinphob_r$PA_outcome)

PAout_subg <- rma.mv(yi = z, 
                      V = var.z,
                      slab = author, 
                      data = Kinphob_r,
                      random = ~ 1 | author/cor_id, 
                      test = "t", 
                      method = "REML",
                      mods = ~ PA_outcome)

summary(PAout_subg)
```


```{r PA outcome meta-analysis meta, warning=FALSE}
PAout <- update(m, 
       subgroup = PA_outcome, 
       tau.common = TRUE)
PAout
```

```{r PA outcome subgroup forest plot, fig.height=25, fig.width=12}
forest(PAout, 
            layout = "RevMan5", 
            common = FALSE, 
            xlim = c(-1.0, 0.6), 
            prediction = TRUE, 
            fs.hetstat = 10, 
            col.subgroup = 'black',
            addrows.below.overall = 2)
```

```{r Save PA outcome forestplot}
png(file = "PA outcome forestplot.png", 
    width = 2800, height = 6400, res = 300)

forest(PAout, 
            layout = "RevMan5", 
            sortvar = -TE, 
            common = FALSE, 
            xlim = c(-1.0, 0.6), 
            prediction = TRUE, 
            fs.hetstat = 10, 
            col.subgroup = 'black',
            addrows.below.overall = 2)

dev.off()
```


## Subgroup analysis by kinesiophobia measure

```{r Subgroup analysis by Kinesiophobia measure}
Kinphob_r$Kinesiophobia_measure <- as.factor(Kinphob_r$Kinesiophobia_measure)

Kines_subg <- rma.mv(yi = z, 
                      V = var.z,
                      slab = author, 
                      data = Kinphob_r,
                      random = ~ 1 | author/cor_id, 
                      test = "t", 
                      method = "REML",
                      mods = ~ Kinesiophobia_measure)

summary(Kines_subg)
```



```{r Kinesiophobia measure subgroup analysis meta}
Kin_sub <- update(m, 
       subgroup = Kinesiophobia_measure, 
       tau.common = TRUE)
Kin_sub
```

```{r Forest plot for subgroup by kinesiophobia tool, fig.height=26, fig.width=10}
forest(Kin_sub, 
      layout = "Revman5", 
      common = FALSE, 
      xlim = c(-1.0, 0.6), 
      prediction = TRUE, 
      fs.hetstat = 10, 
      col.subgroup = 'black',
      addrows.below.overall = 2)
```

```{r Save Kinesiophobia measure forestplot}
png(file = "Kinesiophobia outcome forestplot.png", 
    width = 2800, height = 7000, res = 300)

forest(Kin_sub, 
        layout = "RevMan5", 
        sortvar = -TE, 
        common = FALSE, 
        xlim = c(-1.0, 0.6), 
        prediction = TRUE, 
        fs.hetstat = 10, 
        col.subgroup = 'black',
        addrows.below.overall = 2)

dev.off()
```


# Meta-analysis: meta-regression

## Meta-regression by age

```{r Meta-regression by age}
m.cor.reg.age <- metareg(m, ~Age)
m.cor.reg.age
```

Age did not statistically influence the correlation estimates of the meta-analysis studies (k = 72; p = 0.349).


```{r Bubble plot for meta-regression by age, fig.height=6, fig.width=8}
bubble(m.cor.reg.age, 
       xlim = c(10, 80), 
       ylim = c(-1.5, 0.5),
       xlab = 'Age (years)',
       font.lab = 2,
       studlab = FALSE, # change to TRUE for study labels 
       cex = 2, 
       cex.studlab = 0.6, 
       pos.studlab = 1, 
       offset = 0.5, 
       col.line = 'red')
```

## Meta-regression by proportion of women

```{r Meta-regression by proportion of women}
m.cor.reg.women <- metareg(m, ~Prop_women)
m.cor.reg.women
```

Similarly, the proportion of women (k = 72; p = 0.555) and the mean level of pain in the studies (k = 49; p = 0.481) did not influence correlation estimates. 

```{r Bubble plot for meta-regression by proportion of women, fig.height=6, fig.width=8}
bubble(m.cor.reg.women, 
       xlim = c(-0.1, 1.1), 
       ylim = c(-1.5, 0.5), 
       xlab = 'Proportion of women',
       font.lab = 2,
       studlab = F, 
       cex = 2, 
       cex.studlab = 0.6, 
       pos.studlab = 1, 
       offset = 0.5, 
       col.line = 'red')
```

## Meta-regression by pain

```{r Meta-regression by pain}
m.cor.reg.pain <- metareg(m, ~Pain)
m.cor.reg.pain
```

```{r Bubble plot for meta-regression by pain, fig.height=6, fig.width=8}
bubble(m.cor.reg.pain, 
       xlim = c(-1, 100), 
       ylim = c(-1.5, 0.5), 
       xlab = 'Pain',
       studlab = FALSE, 
       font.lab = 2,
       cex = 2, 
       cex.studlab = 0.6, 
       pos.studlab = 1, 
       offset = 0.5, 
       col.line = 'red')
```

# Sensitivity analysis: meta-regression by axis score

```{r Meta-regression by axis score}
m.cor.reg.axis <- metareg(m, ~quality)
m.cor.reg.axis
```

A study's quality score (k = 83) did not influence correlation values (p = 0.3732).

```{r Bubble plot for meta-regression by axis score, fig.height=6, fig.width=8}
bubble(m.cor.reg.axis, 
       xlim = c(0, 10), 
       ylim = c(-1.5, 0.5), 
       xlab = 'quality',
       studlab = FALSE, 
       font.lab = 2,
       cex = 1.5, 
       cex.studlab = 0.6, 
       pos.studlab = 1, 
       offset = 0.5, 
       col.line = 'red')
```

# Publication bias analysis

## Small-study effects

### Funnel plot 

```{r Contour-enhanced funnel plot for main analysis without labels, fig.height=6, fig.width=8}
# Define fill colors for contour
col.contour = c("gray85", "gray75")

# Funnel plot
meta::funnel(m, 
             xlim = c(-1.5, 1),
             contour = c(0.95, 0.99),
             col.contour = col.contour)

# legend
legend(x =0.5, y = 0.01, 
       legend = c("p < 0.05", "p < 0.01"),
       fill = col.contour)

# title
title("Contour-Enhanced Funnel Plot (Kinesiophobia and Physical Activity)")
```


```{r Save funnel plot}
png(file = "Funnel Plot.png", width = 2500, height = 2000, res = 300)

# Define fill colors for contour
col.contour = c("gray85", "gray75")

# Funnel plot
meta::funnel(m, 
             xlim = c(-1.5, 1),
             contour = c(0.95, 0.99),
             col.contour = col.contour)

# legend
legend(x =0.5, y = 0.01, 
       legend = c("p < 0.05", "p < 0.01"),
       fill = col.contour)

# title
title("Contour-Enhanced Funnel Plot (Kinesiophobia and Physical Activity)")

dev.off()
```

### Egger's test

There is no direct function to conduct Egger's test for multi-level model. Alternatively, we calculate it by using the standard errors of the effect size estimates as a predictor in the meta-regression. (see: https://rstudio-pubs-static.s3.amazonaws.com/814435_6401e0cceb0b410c8208642dc5ee07f0.html)

```{r Eggers test for main analysis}
test.egger = rma.mv(z,var.z, mod = ~ sqrt(var.z), random =  ~ 1 | author/cor_id, data = Kinphob_r, test = "t")
test.egger
```

Egger’s regression test using the standard errors of the effect size estimates as a predictor in the meta-regression showed that the coefficient of the standard error was significant (b = -1.497, 95% CI: -2.618 to -0.3754, p = 0.0095), suggesting that the data in the funnel plot was asymmetrical. This asymmetry may be explained by publication bias, but also by other potential causes, such as different study procedures and between-study heterogeneity, which was substantial-to-considerable here. 


## Pcurve analysis

```{r pcurve for main analysis}
pcurve(m, effect.estimation = FALSE, N, dmin = 0, dmax = 1)
```

The 83 Pearson’s r correlation values were provided to the p-curve analysis. The observed p-curve included 35 statistically significant results (p < 0.05), 27 of which were highly significant (p < 0.025), and was visually right-skewed. The other results were excluded because they had a p > 0.05. The p-value of the right-skewness test was < 0.001 for both the half curve (curve of p values ≤ 0.025) and the full curve (curve of p values < 0.05), confirming that the p-curve was right-skewed and suggesting that the effect of our meta-analysis is true, i.e., that the effect we estimated is not an artifact caused by selective reporting (e.g., p-hacking) in the literature 120. In addition, the statistical power of the studies that were included in the p-curve analysis was 97% (90% CI: 93 to 98%), suggesting that approximately 90% of the significant results are expected to be replicable.


# References
- Cohen J. Statistical power analysis for the behavioral sciences. 2nd ed.; 1988.  
- Egger M, Davey Smith G, Schneider M, Minder C. Bias in meta-analysis detected by a simple, graphical test. BMJ. 1997;315(7109):629-634. https://doi.org/10.1136/bmj.315.7109.62  
- Higgins JPT, Thompson SG. Quantifying heterogeneity in a meta-analysis. Stat Med. 2002;21(11):1539-1558. https://doi.org/10.1002/sim.1186 
- Knapp G, Hartung J. Improved tests for a random effects meta-regression with a single covariate. Stat Med. 2003;22(17):2693-2710. https://doi.org/10.1002/sim.1482  
- R Core Team. R: A language and environment for statistical computing [Computer software]. Version 4.3.1. Vienna, Austria: Foundation for Statistical Computing; 2023. https://www.r-project.org 
- Schwarzer G. Meta: General package for meta-analysis [R package]. Version 6.5-0; 2023. https://cran.r-project.org/web/packages/meta/meta.pdf 
- Schwarzer G, Carpenter RJ, Rücker G. Metasens: Advanced statistical methods to model and adjust for bias in meta-analysis [R package]. Version 1.5-2; 2023. https://cran.r-pro-ject.org/web/packages/metasens/metasens.pdf  
- Simonsohn U, Nelson LD, Simmons JP. P-curve: A key to the file-drawer. J Exp Psychol Gen. 2014;143(2):534-547. http://doi.org/10.1037/a0033242  
- Viechtbauer W. Bias and efficiency of meta-analytic variance estimators in the random-effects model. J Educ Behav Stat. 2005;30(3):261-293. https://doi.org/10.3102/10769986030003261  
- Viechtbauer W. Conducting meta-analyses in R with the metafor package. J Stat Softw. 2010;36(3):1-48. https://doi.org/10.18637/jss.v036.i03  
- Viechtbauer W. Metafor: Meta-analysis package for R [R package]. Version 4.2-0; 2023. https://cran.r-pro-ject.org/web/packages/metafor/metafor.pdf  
- Viechtbauer, "W. (2023). Metafor: Meta-Analysis Package for R (Version 4.2-0) [R pakage]. https://cran.r-project.org/web/packages/metafor/metafor.pdf  
