---
title: "Meta-Analysis_Kinesiophobia_Physical-Activity"
author: "IM Lahart"
contributor: "MP Boisgontier"
date: "2023-08-04"
output:
  pdf_document:
    latex_engine: xelatex
    toc: yes
    toc_depth: 3
---

# R Markdown file set-up

```{r setup and import data file, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
Kinphob_r <- read.csv("2023-08-02_meta_analysis_kinesiophobia_r.csv", header = TRUE, sep = ",")
```

```{r install and load dmetar, include=FALSE}
if (!require("devtools")) {
  install.packages("devtools")
}
devtools::install_github("MathiasHarrer/dmetar")
library(dmetar)
```

```{r packages, include=FALSE}
#Install tidyverse package if needed for 'glimpse'
if(!require(tidyverse)){install.packages('tidyverse')}
#Load tidyverse package
library(tidyverse)

#Install meta package if needed for meta-analysis
if(!require(meta)){install.packages('meta')}
#Load meta package
library(meta)

#Install metafor package if needed for meta-analysis
if(!require(metafor)){install.packages('metafor')}
#Load metfor package
library(metafor)

#Install dmetar package if needed for meta-analysis
if(!require(dmetar)){install.packages('dmetar')}
#Load metfor package
library(dmetar)

#Install metasens package if needed for meta-analysis
if(!require(metasens)){install.packages('metasens')}
#Load metfor package
library(metasens) #Ian, it seems the limitmeta() function requires this package
```

# Data file glimpse (not included in PDF)

```{r glimpse, include=FALSE}
glimpse(Kinphob_r)
```

# Meta-analysis method

In our meta-analysis, we pooled Pearson product-moment correlations from eligible studies to examine the relationship between kinesiophobia and physical activity. When a study measured physical activity with both a questionnaire and accelerometers, the correlation included in the analysis was that of the most reliable outcome, i.e., the accelerometer-based outcome. Correlations were pooled using the generic inverse pooling method via the ‘metacor’ function in the R ‘meta’ package (Schwarzer, 2023). This function automatically performs a necessary Fisher’s z-transformation on the original, untransformed correlations prior to pooling. The ‘metacor’ function also reconverts the pooled association back to its original form for ease of interpretation.

We anticipated considerable between-study heterogeneity, and therefore used a random-effects model to pool correlations. The restricted maximum likelihood (RML) estimator (Viechtbauer, 2005) was used to calculate the heterogeneity variance Tau2. In addition to Tau2, to quantify between-study heterogeneity, we also reported the I2 statistic, which provides the percentage of variability in the correlations that is not caused by sampling error (Higgins and Thompson, 2002). The I2 statistic was interpreted as follows: 0-40%, may not be important; 30-60%, may represent moderate heterogeneity; 50-90%, may represent substantial heterogeneity; and 75-100%, may represent considerable heterogeneity. To reduce the risk of false positives, we used a Knapp-Hartung adjustment (Knapp and Hartung, 2003) to calculate the confidence interval around the pooled association. We also report the prediction interval, which provides a range within which we can expect the associations of future studies to fall based on the current evidence. The pooled correlation was interpreted using Cohen’s conventions (Cohen, 1988): r ≈ -0.10, small negative correlation; r ≈ -0.30, moderate negative correlation; r ≈ -0.50, large negative correlation. Egger’s regression test of funnel plot asymmetry (Egger et al., 1997) and a p-curve analysis (Simonsohn et al., 2014) were conducted to assess potential publication bias in our meta-analysis. The Rücker’s limit meta-analysis method (Schwazer et al., 2023), which explicitly includes the heterogeneity variance in the model, was used to compute bias-corrected estimate of the true effect size.

We conducted subgroup analyses to examine the differences in correlations between studies including participants with different health conditions and using different types of physical activity measures (i.e., device-based versus self-reported), physical activity measurement instruments (i.e., type of questionnaires, type of devices), physical activity outcomes, and kinesiophobia measures. In addition, we used meta-regressions to examine if the average age of participants or the proportion of women in a study predicted the reported correlation between kinesiophobia and physical activity. A secondary meta-analysis was conducted using the same approach, but based on Spearman’s rho values, to further test the relationship between kinesiophobia and device-based physical activity.

All analyses were performed in RStudio integrated development environment (IDE) (2023.06.1+524, “Mountain Hydrangea” release) for R software environment (R Core Team, 2023) using the ‘meta’ (Schwarzer, 2023), ‘metasens’ (Schwarzer et al., 2023), and ‘metafor’ (Vietchbauer, 2010, 2023) R packages.

# Meta-analysis: main results

```{r meta-analysis RE REML and Knapp-Hartung adjustment}
m.cor <- metacor(cor = cor, 
                 n = n,
                 studlab = author,
                 data = Kinphob_r,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Kinesiophobia and physical activity behaviour")
summary(m.cor)
```

Our meta-analysis of 41 studies (n = 4,848) revealed a statistically significant moderate negative correlation between kinesiophobia and physical activity (r = -0.31; 95% confidence interval [95% CI]: -0.42 to -0.20; p < 0.0001; Figure 2). However, we observed considerable between-study statistical heterogeneity (Tau2 = 0.12, 95% CI: 0.08 to 0.22; I2 = 91.8%, 95% CI: 89.9 to 93.5%), and the prediction interval ranged from r = -0.78 to 0.37, indicating that a moderate positive correlation cannot be ruled out for future studies.


```{r Forest plot kinesiophobia and PA, fig.height=10, fig.width=7}

forest.meta(m.cor, 
            layout = "Revman5",
            sortvar = -TE,
            prediction = TRUE, 
            print.tau2 = FALSE,
            leftlabs = c("Author", "n"),
            xlim=c(-1.0,1.0),
            fs.hetstat = 10,
            addrows.below.overall = 2)
```

```{r Save Forest plot main analysis}
png(file = "Main analysis forestplot.png", width = 2800, height = 3800, res = 300)

forest.meta(m.cor, 
            layout = "Revman5",
            sortvar = -TE,
            prediction = TRUE, 
            print.tau2 = FALSE,
            leftlabs = c("Author", "n"),
            xlim=c(-1.0,1.0),
            fs.hetstat = 10,
            addrows.below.overall = 2)

dev.off()
```


```{r}
Kinphob_rho <- data.frame(author <- c("Carvalho, 2017", "Yuksel Karsli, 2019a", "Yuksel Karsli, 2019b", "Ohlman, 2018", "Verbunt, 2005"),
      cor <- c("-0.15", "-0.158", "0.013", "-0.29", "0.06"),
      n <- c("119", "34", "33", "52", "123")
      )
Kinphob_rho$cor <- as.numeric(Kinphob_rho$cor)
Kinphob_rho$n <- as.numeric(Kinphob_rho$n)
```

```{r}
m.cor.rho <- metacor(cor = cor, 
                 n = n,
                 studlab = author,
                 data = Kinphob_rho,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE)
summary(m.cor.rho)
```

```{r}
forest.meta(m.cor.rho, 
            layout = "Revman5",
            sortvar = -TE,
            prediction = TRUE, 
            print.tau2 = FALSE,
            leftlabs = c("Author", "n"),
            xlim=c(-1.0,1.0),
            fs.hetstat = 10,
            addrows.below.overall = 2)
```

```{r Save Forest plot rho analysis}
png(file = "Rho analysis forestplot.png", width = 2100, height = 1000, res = 300)

forest.meta(m.cor.rho, 
            layout = "Revman5",
            sortvar = -TE,
            prediction = TRUE, 
            print.tau2 = FALSE,
            leftlabs = c("Author", "n"),
            xlim=c(-1.0,1.0),
            fs.hetstat = 10,
            addrows.below.overall = 2)

dev.off()
```


## Publication bias analysis

### Funnel plot for small-study effects

```{r funnel plot for main analysis, fig.height=6, fig.width=8}
# Produce funnel plot
funnel.meta(m.cor,
            xlim = c(-1.5, 0.5),
            ylim = c(0.31, 0.0),
            studlab = TRUE,
            cex = 1,
            cex.studlab = 0.6, 
            pos.studlab = 1, 
            offset = 0.5)
```

```{r Save funnel plot}
png(file = "Funnel Plot.png", width = 2100, height = 1500, res = 300)

funnel.meta(m.cor,
            xlim = c(-1.5, 0.5),
            ylim = c(0.31, 0.0),
            studlab = TRUE,
            cex = 1,
            cex.studlab = 0.6, 
            pos.studlab = 1, 
            offset = 0.5)

dev.off()
```

```{r Egger test for main analysis}
metabias(m.cor, method.bias = "linreg")
eggers.test(m.cor)
```

###  Limit meta-analysis 
```{r Rücker Limit Meta-Analysis Method}
limitmeta(m.cor)
```

### Pcurve analysis #Ian, could you please add a csv output of the p-curve figure?

```{r pcurve for main analysis}
pcurve(m.cor, effect.estimation = FALSE, N, dmin = 0, dmax = 1)
```

# Meta-analysis: subgroup analyses

## Subgroup analysis by health status

```{r Subgroup analysis by health status}
Kinphob_r$Health_status <- as.factor(Kinphob_r$Health_status)

Health_subg <- update.meta(m.cor, 
            subgroup = Health_status,
            tau.common = TRUE)
Health_subg
```

The test of subgroup differences between health status measures was possible between studies comprising people with chronic pain (k = 11), cardiovascular disease (k = 11), arthritis (k = 6), and neurological conditions (k = 2), people who had received surgery (k = 4), and older adults (k = 3) (Figure 3D). We found statistical differences between these studies (p < 0.0001). The relationship between kinesiophobia and physical activity was statistically significant only in studies that included participants with cardiovascular disease (r = -0.47; 95% CI: -0.59 to -0.32) and arthritis (r = -0.42; 95% CI: -0.69 to -0.05). The effect of arthritis remained non-significant when focusing on osteoarthritis (k = 5) (r = -0.48; 95% CI: -0.76 to -0.35). Statistical heterogeneity was higher in the studies comprising people with arthritis (I2 = 92.7%) than the ones studies comprising people with cardiovascular disease (I2 = 83.9%). 

```{r Forest plot for subgroup by Health condition, fig.height=18, fig.width=9}
forest.meta(Health_subg, 
            layout = "RevMan5", 
            sortvar = -TE, 
            common = FALSE, 
            xlim = c(-1.0, 0.5), 
            prediction = TRUE, 
            fs.hetstat = 10, 
            addrows.below.overall = 2)
```

```{r Save Health condition forestplot}
png(file = "Health condition forestplot.png", width = 2800, height = 5600, res = 300)

forest.meta(Health_subg, 
            layout = "Revman5", 
            sortvar = -TE, 
            common = FALSE, 
            xlim = c(-1.0, 0.5), 
            prediction = TRUE, 
            fs.hetstat = 10, 
            addrows.below.overall = 2)

dev.off()
```


## Subgroup analysis by physical activity measure: device vs self-report 

```{r Subgroup analysis by PA objectivity}
Kinphob_r$PA_objectivity <- as.factor(Kinphob_r$PA_objectivity)

PAobj_subg <- update.meta(m.cor, 
            subgroup = PA_objectivity, 
            tau.common = TRUE)
PAobj_subg
```

The test of subgroup differences between self-reported (k = 32) and device-based (k = 9) measures of physical activity showed a statistical difference between these groups (p = 0.011), with only the self-reported measures showing a statistical correlation (r = -0.36; 95% CI: -0.48 to -0.24)  (Figure 3B). However, we observed considerable between-study statistical heterogeneity (I2 = 92.9%).

```{r PA measure objectivity subgroup forest plot, fig.height=14, fig.width=7}
forest.meta(PAobj_subg, 
            layout = "RevMan5", 
            sortvar = -TE, 
            common = FALSE, 
            xlim = c(-1.0, 0.5), 
            prediction = TRUE, 
            fs.hetstat = 10, 
            addrows.below.overall = 2)
```

```{r Save PA objectivity forestplot}
png(file = "PA objectivity forestplot.png", width = 2800, height = 4500, res = 300)

forest.meta(PAobj_subg, 
            layout = "Revman5", 
            sortvar = -TE, 
            common = FALSE, 
            xlim = c(-1.0, 0.5), 
            prediction = TRUE, 
            fs.hetstat = 10, 
            addrows.below.overall = 2)

dev.off()
```


## Subgroup analysis by kinesiophobia measure

```{r Subgroup analysis by Kinesiophobia measure}
Kinphob_r$Kinesiophobia_measure <- as.factor(Kinphob_r$Kinesiophobia_measure)

Kines_subg <- update.meta(m.cor, 
            subgroup = Kinesiophobia_measure, 
            tau.common = TRUE)
Kines_subg
```

The test of subgroup differences between kinesiophobia measures was possible only for TSK-17 (k = 21), TSK-Heart (k = 11), and TSK-11 (Figure 3A), with only the former ones showing a statistical correlation. The correlation was stronger in studies using the TSK-Heart (r = -0.59; 95% CI: -0.75 to -0.36) than with the TSK-17 (r = -0.28; 95% CI: -0.43 to -0.11). Heterogeneity was lower, albeit substantial to considerable heterogeneity in the studies using TSK-Heart (I2 = 85.0%) than TSK-17 (I2 = 92.6%).

```{r Forest plot for subgroup by kinesiophobia tool, fig.height=16, fig.width=7}
forest.meta(Kines_subg, 
            layout = "Revman5", 
            sortvar = -TE, 
            common = FALSE, 
            xlim = c(-1.0, 0.5), 
            prediction = TRUE, 
            fs.hetstat = 10, 
            addrows.below.overall = 2)
```

```{r Save Kinesiophobia measure forestplot}
png(file = "Kinesiophobia measure forestplot.png", width = 2800, height = 4700, res = 300)

forest.meta(Kines_subg, 
            layout = "Revman5", 
            sortvar = -TE, 
            common = FALSE, 
            xlim = c(-1.0, 0.5), 
            prediction = TRUE, 
            fs.hetstat = 10, 
            addrows.below.overall = 2)

dev.off()
```

## Subgroup analysis by physical activity measure

```{r Subgroup analysis by PA measure}
Kinphob_r$PA_measure <- as.factor(Kinphob_r$PA_measure)

PAmeas_subg <- update.meta(m.cor, 
            subgroup = PA_measure, 
            tau.common = TRUE)
PAmeas_subg
```

The test of subgroup differences between physical activity measures described more specifically was possible between studies using the IPAQ (k = 18), MLTPAQ (k = 2), GLTEQ (k = 2), BHPAQ (k = 2), as well as accelerometers (k = 8) and pedometers (k = 2). We found statistical differences between these studies (p = 0.014). The relationship between kinesiophobia and physical activity was statistically significant only in studies that used the IPAQ to measure physical activity (r = -0.43; 95% CI: -0.57 to -0.26). However, we observed considerable between-study statistical heterogeneity (I2 = 89.7%). 

```{r Forest plot for subgroup by PA measure, fig.height=18, fig.width=9}
forest.meta(PAmeas_subg, 
            layout = "Revman5", 
            sortvar = -TE, 
            common = FALSE, 
            xlim = c(-1.0, 0.5), 
            prediction = TRUE, 
            fs.hetstat = 10, 
            addrows.below.overall = 2)
```
```{r Save PA measure forestplot}
png(file = "Physical activity measure forestplot.png", width = 2800, height = 5600, res = 300)

forest.meta(PAmeas_subg, 
            layout = "Revman5", 
            sortvar = -TE, 
            common = FALSE, 
            xlim = c(-1.0, 0.5), 
            prediction = TRUE, 
            fs.hetstat = 10, 
            addrows.below.overall = 2)

dev.off()
```

## Subgroup analysis by physical outcome

```{r Subgroup analysis by PA outcome}
Kinphob_r$PA_outcome <- as.factor(Kinphob_r$PA_outcome)

PAout_subg <- update.meta(m.cor, 
            subgroup = PA_outcome, 
            tau.common = TRUE)
PAout_subg
```

The test of subgroup differences between physical activity outcomes was possible between studies using MET-min/week from the IPAQ (k = 16), a score from a questionnaire (k = 10), steps/day (k = 4), low versus high level of physical activity (k = 4), counts/min (k =3), and a dichotomous assessment of physical activity level (low vs. high) (k = 2) (Figure 3C). We observed statistical differences between these studies (p = 0.0002), with only the studies using the MET-min/week  (r = -0.45; 95% CI: -0.60 to -0.26) or score outcome (r = -0.33; 95% CI: -0.57 to -0.02) showing a statistical correlation. Heterogeneity was considerable in studies relying on these outcomes (I2 = 90.7 and 95.5%, respectively).
Results of these sensitivity analyses are consitent with the main results suggesting that the relationship between kinesiophobia and physical activity is observed only when self-reporeted measures of physical activity are used.

```{r PA outcome subgroup forest plot, fig.height=18, fig.width=9}
forest.meta(PAout_subg, 
            layout = "RevMan5", 
            sortvar = -TE, 
            common = FALSE, 
            xlim = c(-1.0, 0.5), 
            prediction = TRUE, 
            fs.hetstat = 10, 
            addrows.below.overall = 2)
```

```{r Save PA outcome forestplot}
png(file = "PA outcome forestplot.png", width = 2800, height = 5600, res = 300)

forest.meta(PAout_subg, 
            layout = "Revman5", 
            sortvar = -TE, 
            common = FALSE, 
            xlim = c(-1.0, 0.5), 
            prediction = TRUE, 
            fs.hetstat = 10, 
            addrows.below.overall = 2)

dev.off()
```

# Meta-analysis: meta-regression

## Meta-regression by age

```{r Meta-regression by age}
m.cor.reg.age <- metareg(m.cor, ~Age)
m.cor.reg.age
```

Age did not statistically influence the correlation values of the meta-analysis studies (k = 31) (Figure 4A). Due to the similar I2 between this meta-regression and the main meta-analysis (92.6% vs. 91.8%, respectively), the addition of age as predictor did not explain the considerable heterogeneity observed between study correlations. The R2 revealed that only 1.0% of the differences between study correlations could be explained by age.

```{r Bubble plot for meta-regression by age, fig.height=6, fig.width=8}
bubble(m.cor.reg.age, 
       xlim = c(15, 80), 
       ylim = c(-1.5, 0.5),
       xlab = 'Age (years)',
       font.lab = 2,
       studlab = TRUE, 
       cex = 2, 
       cex.studlab = 0.6, 
       pos.studlab = 1, 
       offset = 0.5, 
       col.line = 'red')
```

## Meta-regression by proportion of women

```{r Meta-regression by proportion of women}
m.cor.reg.women <- metareg(m.cor, ~Prop_women)
m.cor.reg.women
```

Similarly, the proportion of women (k = 33) and the mean level of pain in the studies (k = 23) did not influence correlation values (Figure 4B and 4C, respectively). The R2 revealed that these variables explained less than 0.01% of the differences between study correlations.

```{r Bubble plot for meta-regression by proportion of women, fig.height=6, fig.width=8}
bubble(m.cor.reg.women, 
       xlim = c(-0.1, 1.1), 
       ylim = c(-1.5, 0.5), 
       xlab = 'Proportion of women',
       font.lab = 2,
       studlab = TRUE, 
       cex = 2, 
       cex.studlab = 0.6, 
       pos.studlab = 1, 
       offset = 0.5, 
       col.line = 'red')
```

## Meta-regression by pain

```{r Meta-regression by pain}
m.cor.reg.pain <- metareg(m.cor, ~Pain)
m.cor.reg.pain
```

```{r Bubble plot for meta-regression by pain, fig.height=6, fig.width=8}
bubble(m.cor.reg.pain, 
       xlim = c(-1, 100), 
       ylim = c(-1.5, 0.5), 
       xlab = 'Pain',
       studlab = TRUE, 
       font.lab = 2,
       cex = 2, 
       cex.studlab = 0.6, 
       pos.studlab = 1, 
       offset = 0.5, 
       col.line = 'red')
```

# References

- Cohen J. Statistical power analysis for the behavioral sciences. 2nd ed.; 1988.  
- Egger M, Davey Smith G, Schneider M, Minder C. Bias in meta-analysis detected by a simple, graphical test. BMJ. 1997;315(7109):629-634. https://doi.org/10.1136/bmj.315.7109.62  
- Higgins JPT, Thompson SG. Quantifying heterogeneity in a meta-analysis. Stat Med. 2002;21(11):1539-1558. https://doi.org/10.1002/sim.1186  
- Knapp G, Hartung J. Improved tests for a random effects meta-regression with a single covariate. Stat Med. 2003;22(17):2693-2710. https://doi.org/10.1002/sim.1482  
- R Core Team. R: A language and environment for statistical computing [Computer software]. Version 4.3.1. Vienna, Austria: Foundation for Statistical Computing; 2023. https://www.r-project.org 
- Schwarzer G. Meta: General package for meta-analysis [R package]. Version 6.5-0; 2023. https://cran.r-project.org/web/packages/meta/meta.pdf 
- Schwarzer G, Carpenter RJ, Rücker G. Metasens: Advanced statistical methods to model and adjust for bias in meta-analysis [R package]. Version 1.5-2; 2023. https://cran.r-pro-ject.org/web/packages/metasens/metasens.pdf  
- Simonsohn U, Nelson LD, Simmons JP. P-curve: A key to the file-drawer. J Exp Psychol Gen. 2014;143(2):534-547. http://doi.org/10.1037/a0033242  
- Viechtbauer W. Bias and efficiency of meta-analytic variance estimators in the random-effects model. J Educ Behav Stat. 2005;30(3):261-293. https://doi.org/10.3102/10769986030003261  
- Viechtbauer W. Conducting meta-analyses in R with the metafor package. J Stat Softw. 2010;36(3):1-48. https://doi.org/10.18637/jss.v036.i03  
- Viechtbauer W. Metafor: Meta-analysis package for R [R package]. Version 4.2-0; 2023. https://cran.r-pro-ject.org/web/packages/metafor/metafor.pdf  
- Viechtbauer, "W. (2023). Metafor: Meta-Analysis Package for R (Version 4.2-0) [R pakage]. https://cran.r-project.org/web/packages/metafor/metafor.pdf  
